Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-09 W13report.tex
Added comments to summary to clarify some issues for M. Strauss.

\maketitle
\vspace{-2ex}
We provide here a technical report on the LSST Data Management
late--Winter 2013 production runs.  This production focused on the
evaluation of LSST DM image differencing code and, in particular, 
the rate of false detections the pipeline generates.  As
inputs, we used a suite of simulated images generated in semi-idealized
conditions and containing no intrinsic variability.  Thus {\it any}
sources detected in these image differences are ``false positives''.

@@

>>>>

\maketitle
\vspace{-2ex}
We provide here a technical report on the LSST Data Management
late--Winter 2013 production runs.  This production focused on the
evaluation of LSST DM image differencing code and, in particular, 
the rate of false detections the pipeline generates.  As
inputs, we used a suite of simulated images generated in semi-idealized
(stars only, no saturation, cosmic rays, or defects) conditions and containing no intrinsic variability.  
Thus {\it any}
sources detected in these image differences are ``false positives''.

@@

Please address any questions about this document to LSST-data@lsstcorp.org.
